Highlighting Disputed Claims on the Web

### 2009-10-27 papers/www_disputefinder/disputefinder.tex
Playing with the user study section

\item[Client-side entailment:] The browser extension runs a simple textual entailment algorithm over all sentences on every web page the user browse, checking to see if any sentence on the page entails any claim in the database (Figure~\ref{nlp_client_server}). A user can enter additional paraphrases of a claim to help the entailment algorithm. This is the implementation used by the currently released version of Dispute Finder (Figure~\ref{paraphrases}).
\end{description}

@@

The Design of Dispute Finder has been influenced by several different kinds of input from potential users. We performed a series of "think aloud" user studies to evaluate the user interface, we circulated a survey among members of a local debate club, and we performed a series of interviews with people selected from those who completed the survey.

\subsection{Survey}

We circulated a survey amongst members of a local debate club - a set of people who we believe is a good match for our Skeptical Reader and Activist personas. They survey asked respondants to tell us how often they typically engaged in various behaviours on the web. Although the survey was too small to be statistically useful, the results gave some useful information that we believe is worth reporting.

Most people 65\% said that some of the information they read is not trustworthy, but they know which sites they can trust. Nobody said that they trusted the most of the information they read. 17\% trust very little of the information they read, and 9\% feel confused about what they can trust.

Everyone had used another source to double-check information they had read online. 74\% "often" search the web to find web pages that confirm a claim they have read. 64\% "often" check a website they trust. 55\% "sometimes" ask a friend and 55\% "sometimes" check a book.

When deciding whether to trust a web site, the most important factor was whether the site was run by an organization they trusted (61\% often, 30\% sometimes), followed by whether the site was linked from another site they trusted (18\%,50\%), and whether the site was well written (18\%,50\%).

% \subsection{Interviews}

\todo{Do we have enough interview content to integrate it? Probably not yet...}
\todo{Is the survey interesting enough to quote here? Only 23 people, and not exciting. Just quote inline with findings.}

\subsection{Think-Aloud User Studies}

@@

\subsubsection{Procedure}

@@

@@

Most users were able to use Dispute Finder compentently as a skeptical reader (browsing information about disputed claims) but found it harder to act compentently as an activist (adding new disputed claims).

When browsing a page that had disputed claims highlighted, most users correctly inferred that these were sentences they should be skeptical about, but some users thought that we were saying they were wrong, rather than merely disputed. Not all users realised that one could click on a disputed claim to bring up more information.

@@

When asked to mark snippets on a particular page that make disputed claims, users often did not appreciate that they should either re-use existing claims or create claims that would be applicable to snippets on many other pages. Several users tried to create a new claim with exactly the same text as the snippet they were marking, and several users asked why they had to "enter the text again". Similarly, users got confused when a snippet made two different disputed claims. The correct behavior is to mark the same text with two different claims, but several participants tried to create a new compound claim such as "Global warming will cause X and Y".

Conversely, when adding a claim to the Dispute Finder web site, users would often enter claims that are not disputed anywhere on the web, or enter paraphrases that do not resemble the wording used on any web site. The challenge of how to help users come up with claims that occur on many web sites is one that we have not yet solved.

Several users expressed confusion about how specific a claim they created should be. For example, if a snippet says ``Global temperatures will rise by X degrees by 2050'' then is that making the claim ``Global temperatures will rise'', or should the claim include the extra information? In order to make a good judgement, one needs to know the range of similar claims that are being made by other web sites, and what claims one has good evidence against. If one makes the claim too specific then one will be able to find less web pages that make it, but if one makes the claim too general then it might be harder to find solid evidence against it.

@@

In the first two studies, the popup interface for a claim showed an argumentation graph. This graph connected the graphs in our database using "supports" or "opposes" links, and allowed each claim to also be associated with supporting articles.

When shown an argumentation graph for a claim, users seemed to have little difficulty navigating and understanding it and appreciated the ability to explore the structure of an argument and see how different claims were connected. One user said "I can see myself getting addicted to this", and another said "it's very intuitivet".

Users seemed to have difficulty creating such graph structures however. Some users linked one claim as supporting another when it would have been more logically correct for them to both support a third claim. For example "Global warming is causing more hurricanes" does not support "Global warming is causing rising sea levels", but both support "Global warming is causing problems". Users correctly realised that the claims were related, but were not sure how best to connect them. Some users were confused by claims that had a ``because'' relationship rather than a ``supports'' or ``opposes'' relationship. For example ``America did not sign the Kyoto Protocol'' {\it because} ``Signing Kyoto would harm the US economy''. It is possible that creating logically correct claim structures may be too difficult for some people (see Isenmann and Reuter~\cite{Isenmann1997}).

@@

Several users expressed an interest in being able to add a disputed claim without having to find opposing evidence. One user said that opposing a claim required ``too many clicks'' and they wanted to be able to just vote against a claim without having to say why or find evidence.

@@

The biggest problem that Dispute Finder has right now is that it is rare that Dispute Finder will highlight a snippet that makes a claim that the user did not already know was disputed. This is for two reasons: our database of disputed claims is currently too small (around two thousand claims at the time of writing), and our textual entailment algorithm is not sufficiently sophisticated to stand a good chance of highlighting snippets when they make those claims.

\todo{Need to say that the argumentation graph contains all existing claims and that it was a simple "supports"/"oppsose" graph.}.

@@

An experimental preview version of Dispute Finder is available at the following URL:
\url{http://disputefinder.org}

@@

\section{Acknowledgments}

>>>>

\item[Client-side entailment:] The browser extension runs a simple textual entailment algorithm over all sentences on every web page the user browse, checking to see if any sentence on the page entails any claim in the database (Figure~\ref{nlp_client_server}). A user can enter additional paraphrases of a claim to help the entailment algorithm (Figure~\ref{paraphrases}). This is the implementation used by the currently released version of Dispute Finder.
\end{description}

@@

%The Design of Dispute Finder has been influenced by several different kinds of input from potential users. We performed a series of "think aloud" user studies to evaluate the user interface, we circulated a survey among members of a local debate club, and we performed a series of interviews with people selected from those who completed the survey.
%
%\subsection{Survey}
%
%We circulated a survey amongst members of a local debate club - a set of people who we believe is a good match for our Skeptical Reader and Activist personas. They survey asked respondants to tell us how often they typically engaged in various behaviours on the web. Although the survey was too small to be statistically useful, the results gave some useful information that we believe is worth reporting.
%
%Most people 65\% said that some of the information they read is not trustworthy, but they know which sites they can trust. Nobody said that they trusted the most of the information they read. 17\% trust very little of the information they read, and 9\% feel confused about what they can trust.
%
%Everyone had used another source to double-check information they had read online. 74\% "often" search the web to find web pages that confirm a claim they have read. 64\% "often" check a website they trust. 55\% "sometimes" ask a friend and 55\% "sometimes" check a book.
%
%When deciding whether to trust a web site, the most important factor was whether the site was run by an organization they trusted (61\% often, 30\% sometimes), followed by whether the site was linked from another site they trusted (18\%,50\%), and whether the site was well written (18\%,50\%).
%
%% \subsection{Interviews}
%
%\todo{Do we have enough interview content to integrate it? Probably not yet...}
%\todo{Is the survey interesting enough to quote here? Only 23 people, and not exciting. Just quote inline with findings.}

@@

\subsection{Procedure}

@@

We also conducted interviews with most of our user study participants, and six additional people, asking them how they use the web to form and promote their opinions.

@@

Most users were able to use Dispute Finder compentently as a skeptical reader (browsing information about disputed claims) but found it harder to act compentently as an activist (adding new disputed claims). Several participants wanted to see Dispute Finder work for them as a skeptical reader before dedicating time to adding and curating new claims ("I want to see it work before I add stuff").

When browsing a page that had disputed claims highlighted, most users correctly inferred that these were sentences they should be skeptical about, but some users thought that we were saying they were wrong, rather than merely disputed. Not all users realised that one could click on a disputed claim to bring up more information. Several users complained about Dispute Finder highlighing snippets that weren't making the claim Dispute Finder indicated.

@@

When marking a snippet on a particular page, users often did not appreciate that a claim should apply to more than one snippet. Several users tried to create a new claim with exactly the same text as the snippet they were marking, and several users asked why they had to "enter the text again". Similarly, several users got confused when a snippet made two different disputed claims. The correct behavior is to mark the same text with two different claims, but several participants tried to create a new compound claim such as "Global warming will cause X and Y".

Conversely, when adding a claim to the Dispute Finder web site, users would often enter claims that are not disputed anywhere on the web or enter paraphrases that do not resemble the wording used on any web site. The challenge of how to help users come up with claims that occur on many web sites is one that we have not yet solved.

Several users expressed confusion about how specific a claim they created should be. For example, if a snippet says ``Global temperatures will rise by X degrees by 2050'' then is that making the claim ``Global temperatures will rise'', or should the claim include the extra information? In order to make a good judgement, one needs to know the range of similar claims that are being made by other web sites, and what claims there is good evidence against. If one makes the claim too specific then one will be able to find less web pages that make it, but if one makes the claim too general then it might be harder to find solid evidence against it.

@@

In the first two studies, the popup interface for a claim showed an argumentation graph. This graph connected the graphs in our database using "supports" or "opposes" links, and allowed each claim to also be associated with supporting articles. When shown an argumentation graph for a claim, users seemed to have little difficulty navigating and understanding it and appreciated the ability to explore the structure of an argument and see how different claims were connected. One user said "I can see myself getting addicted to this", and another said "it's very intuitivet".

Users seemed to have difficulty creating such graph structures however. Several users linked one claim as supporting another when it would have been more logically correct for them to both support a third claim. For example "Global warming is causing more hurricanes" does not support "Global warming is causing rising sea levels", but both support "Global warming is causing problems". Users correctly realised that the claims were related, but were not sure how best to connect them. Some users were confused by claims that had a ``because'' relationship rather than a ``supports'' or ``opposes'' relationship. For example ``America did not sign the Kyoto Protocol'' {\it because} ``Signing Kyoto would harm the US economy''. These findings are consistent with those of Isenmann and Reuter~\cite{Isenmann1997}.

@@

Several users expressed an interest in being able to add a disputed claim without having to find opposing evidence. One user said that opposing a claim required ``too many clicks'' and they wanted to be able to just vote against a claim without having to say why or find evidence. Users did however recognize that they would want to see opposing evidence as a reader.

@@

Most people we interviewed were interested in applying Dispute Finder to particular areas that affected them or that they were expected to be knowledgeable about, but were less interested about applying it to pages about other topics, that they were less interested in. For topics that didn't affect them users felt that misinformation was "not important enough to bother with", or that they could "afford to be misinformed".

Most users were frustrated by the relatively poor accuracy and recall that Dispute Finder has at present. Several users browsed to a page that they knew contained disputed claims, and were disappointed when Dispute Finder didn't highlight anything. Several users were also frustrated when Dispute Finder highlighted phrases that did not make the claim Dispute Finder indicated. If Dispute Finder is to be adopted widely then we will need to significantly improve precission and recall, by building a bigger database of disputed claims, and improving the accuracy of our textual entailment algorithm.

\todo{Need to say that the argumentation graph contains all existing claims and that it was a simple "supports"/"oppsose" graph.}

@@

An experimental preview version of Dispute Finder is available at 
\url{http://disputefinder.org}

@@

%\section{Acknowledgments}
